---
geometry: "left=0cm,right=1.5cm,top=0cm,bottom=0cm"
header-includes:
- \usepackage{titling}
- \pretitle{\begin{center}\LARGE\includegraphics[width=3cm]{logo.png}\\[\bigskipamount]}
- \posttitle{\end{center}}
- \usepackage[fontsize=12pt]{scrextend}
- \usepackage{floatrow}
- \usepackage{multicol}
- \usepackage{fontspec}
- \setmainfont{Georgia}
- \floatsetup[figure]{capposition=top}
- \floatsetup[table]{capposition=top}
- \floatplacement{figure}{H}
- \floatplacement{table}{h}

output: 
  bookdown::pdf_document2:
    latex_engine: xelatex
    extra_dependencies: ["color","xcolor","array","ragged2e","wrapfig","multicol","fancyhdr","hyphenat","tikz","amsmath"]
    toc: no
    highlight: tango
    number_sections: TRUE
link-citations: yes
linkcolor: blue
urlcolor: blue
---

\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = TRUE, warning = FALSE, message = FALSE)

```

```{r paquetes, echo=FALSE}
if (! require("pacman")) install.packages("pacman")

pacman::p_load(knitr, 
               tidyverse,
               lubridate,
               scales,
               kableExtra,
               glue,
               here)
```

```{r parametros, echo=FALSE}

```

```{r funciones, echo=FALSE}

miles <- function(x) {
  format(round(as.numeric(x),0), big.mark = ".")
}

decimales <- function(x) {
  format(round(as.numeric(x), 2), decimal.mark = ",")
}

# set theme

theme_nice <- function() {
   theme_bw() +
  theme(legend.position = "top",
        axis.title = element_text(size = 12),
        axis.text.y = element_text(size = rel(1)),
        plot.title = element_text(face = "bold", size = 12),
        axis.text.x = element_text(angle = 90,
                                   vjust = 0.5,
                                   size = rel(1)))


}

theme_set(theme_nice())

```


\renewcommand{\tablename}{Tabla}
\renewcommand{\figurename}{Figura}

\definecolor{naranjodoc}{RGB}{55, 127, 199}
\definecolor{naranjodocoscuro}{RGB}{44, 102, 159}

\begin{tikzpicture}
 \draw [fill=naranjodoc] (0,0) rectangle (14,27.9);
 \draw [fill=naranjodocoscuro] (14,0) rectangle (15,27.9);
 \node[text=naranjodoc, font=\bfseries] at (18.3,25) {\Large Unidad de Estudios};
  \node[text=naranjodoc, font=\bfseries] at (18.3,24) {\Large Laborales};
 \node[right, text=white, font=\bfseries] at (1,17) {\Huge Informe de Resultados};
 \node[right,text=white] at (1,14) {\Large Título };
 
 \draw [fill=white] (0.5,4) rectangle (13.5,4.2);
 \node[right, text=white, font=\bfseries] at (9,2) {Primera versión};
  \node[right, text=white, font=\bfseries] at (9,1.5) {`r lubridate::today()`};
 \node[inner sep=0pt] (ine) at (18.3,4)
    {\includegraphics[width=2in,height=2in]{logo.PNG}};
  \node[text=white] at (18,10) {};
\end{tikzpicture}

\newpage

\newgeometry{left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm}

\newpage

\setcounter{tocdepth}{2}
\renewcommand{\contentsname}{Tabla de contenidos}

\hypersetup{linkcolor=black}
\tableofcontents

\hypersetup{linkcolor=blue}

\newpage
